\section{Appendix: Relevant functions and Identities}\label{s:appendices}
\begin{definition}
    Let \(D\) be the differential operator, such that \(D f(x) = \frac{d}{dx} f(x)\). Then the fractional derivative of order \(\alpha\) is defined as \[D^{\alpha} f(x) = \frac{d^{\alpha}}{dx^{\alpha}} f(x)\]
    \cite{samko1993}
\end{definition}
In this definition, \(\alpha\) can be any real number. When taking regular derivatives, \(\alpha \in \mathbb{N}\). In most of our cases, we are interested in the instance where  \(\alpha \in \mathbb{R}_+\). It is also possible to study derivatives of negative order, which can be used to obtain moments of negative order of a function, provided that such an order exists. A derivative of negative order is simply an integral of positive order. This is defined as follows:
\begin{definition}
    Let \(I\) be the integral operator, such that \(I f(x) = \int f(x) dx\). Then the fractional integral of order \(\alpha\) is defined as \[(I^{\alpha} f) (x) = \frac{1}{(\alpha-1)!}\int (x-t)^{\alpha-1} f(t) dt\] \cite{cauchy1823}.
\end{definition} 

Combining the previous two definitions, we obtain the following, more general, definition.
\begin{definition}\label{d: differintegral}
    The differintegral operator is defined as
    \begin{equation}
        R^\alpha f(x) = \begin{cases}
            I^{|\alpha|} f(x) & \text{if } \alpha < 0 \\
            D^\alpha f(x) & \text{if } \alpha > 0 \\
            f(x) & \text{if } \alpha = 0
        \end{cases}, \text{ with } \alpha \in \mathbb{R}.
        \end{equation}
        \cite{oldham1974}
\end{definition}

We define the (Euler-)Gamma function as follows:
\begin{definition}\label{d: eg}
    for \(\Re(z) > 0\), we have the following: \(\Gamma(z) = \int_{0}^{\infty} t^{z-1} e^{-t} dt\)
\end{definition}

The Gamma function can be seen as an extension of the factorial function, for non-integers. This function is defined for complex numbers and all there subsets (so also real numbers), as long as the condition above holds. For positive integers values \(z\), we have the following identity: \(\Gamma(z) = (z - 1)!\)
Other important identities, not necessarily for \(z\) an integer, are: 
\begin{itemize}
    \item \(\Gamma(z + 1) = z \Gamma(z)\)
    \item \(\Gamma(2) = \Gamma(1) = 1\)
    \item \(\Gamma(\frac{1}{2}) = \sqrt{\pi}\)
\end{itemize}


\begin{definition}
    For \(0 \leq k \leq n\), the Binomial Coefficient is defined as follows: \[\binom{n}{k} = \frac{n!}{k! (n - k)!} = \frac{\Gamma(n + 1)}{\Gamma(k + 1) \cdot \Gamma( n - k  + 1)}\], where \(n, k \in \mathbb{N}\) and \(\Gamma(.)\) as defined in \ref{d: eg}.
\end{definition}


\begin{definition}
    Vandermonde's identity: for non-negative integers, \(k, l, m, n\), we have that \[\sum_{k = 0}^{l} \binom{m}{k} \cdot \binom{n}{l - k} = \binom{m + n}{l}\]
\end{definition}
A modification on the latter identity has been called the Chu-Vandermonde identity. This is the same identity, but it his been proven that the identities still hold for complex values \(m, n\) as long as \(l\) is a positive integer \cite{askey75}.

\begin{definition}\label{d: binomial}
    The binomial series is a generalization of the binomial formula, namely:
    \[(1 + x)^\alpha = \sum_{k = 0}^{\infty}\binom{\alpha}{k} \cdot x^k\]
\end{definition}

For the interchange-ability of derivatives and integrals and sums, we can apply the following two theorems:

\begin{theorem}
    Leibnitz's Rule:
    Let \(f(x, \theta), a(\theta), b(\theta)\) be differentiable with respect to \(\theta\), then we have that:
    \[ \frac{d}{d\theta} \int_{a(\theta)}^{b(\theta)} f(x, \theta) dx = f(b(\theta), \theta) \frac{d b(\theta)}{d\theta} - f(a(\theta), \theta) \frac{d a(\theta)}{d\theta} + \int_{a(\theta)}^{b(\theta)} \frac{\partial f(x, \theta) }{\partial \theta} dx.\] For the special case, where \(a(\theta), b(\theta)\) are constant we have that: 
    \[\frac{d}{d\theta} \int_{a}^{b} f(x, \theta) dx =  \int_{a}^{b} \frac{ \partial f(x, \theta)}{ \partial d\theta}.\]
\end{theorem}

For the interchange-ability of derivatives and summations, the following theorem has been given by \cite{casella2002}:
\begin{theorem}
    Suppose that the series \(\sum_{x = 0}^{\infty} h(\theta, x)\) converges for all \(\theta\) in an interval \((a, b)\) of real numbers and 
    
    \begin{enumerate}[(i)]
        \item \(\frac{\partial h(\theta, x)}{\partial \theta}\) is continuous for all \(x\)
        \item \(\sum_{x = 0}^{\infty} \frac{\partial h(\theta, x)}{\partial \theta}\) converges uniformly on every closed bounded sub-interval of \((a, b)\)
    \end{enumerate}
    Then:
    \[
    \frac{d}{d \theta} \left( \sum_{x = 0}^{\infty} h(\theta, x) \right) = \sum_{x = 0}^{\infty} \frac{\partial h(\theta, x)}{\partial \theta}
    \]
    
   
\end{theorem}


\clearpage
\section{Appendix: Proofs of section \ref{s:methodology}}\label{s:app_B}

\subsection{Proofs section \ref{s:calculus}}

\begin{proof}
    Proof of \ref{p: calculus}
    \begin{enumerate}[(i)]
        \item We will proof for the Riemann-Liouville derivative, the proof for the Caputo-Fabrizio derivative is very similar and the Gr端nwald-Letnikov derivative is a direct consequence of the linearity of the sum.
        \[ D^{\alpha} (a f(x) + b g(x)) = \frac{d^n}{dx^n}\frac{1}{\Gamma(n - \alpha)} \int_{0}^{x} (x - t)^{n - \alpha - 1} \left(a f(t) + b g(t)\right) dt \]
     
        \[= \frac{d^n}{dx^n}\left(\frac{a}{\Gamma(n - \alpha)} \int_{0}^{x} (x - t)^{n - \alpha - 1}  f(t)dt + \frac{b}{\Gamma(n - \alpha)} \int_{0}^{x} (x - t)^{n - \alpha - 1} g(t)dt\right) \] Where we simply split the integral and put the constants in front.
        \[= \frac{d^n}{dx^n}\frac{a}{\Gamma(n - \alpha)} \int_{0}^{x} (x - t)^{n - \alpha - 1}  f(t)dt + \frac{d^n}{dx^n} \frac{b}{\Gamma(n - \alpha)} \int_{0}^{x} (x - t)^{n - \alpha - 1} g(t)dt \] As the regular derivative operator is linear.
        \[ = a D^{\alpha} f(x) + b D^{\alpha} g(x) \]
        \item Intuitively, this makes perfect sense, as the 0-th derivative is just no derivative, so just the function \(f(x)\). But for these derivatives, a little bit more effort is required to prove this rather obvious fact.
        \newline 
        For the Gr端nwald-Letnikov derivative we get: \[D^0 f(x) = \lim_{h \to 0} \frac{1}{h^0} \sum_{k=0}^\infty (-1)^k \binom{0}{k} f(x - k h)
        = \lim_{h \to 0} \frac{1}{1} \sum_{k=0}^\infty (-1)^k \frac{0!}{k!(0- k)!} f(x - k h).\] The factorial identity of the binomial coefficient only holds for \(0 \leq k \leq \alpha\). Since \(\alpha = 0\) and k is always a positive integer lesser or equal to \(\alpha, k = 0\). Thus, we get:
        \[ = \lim_{h \to 0} \sum_{k=0}^\infty (-1)^0 \frac{0!}{0!(0- 0)!} f(x - 0 h) = \lim_{h \to 0} f(x - 0 h) = f(x).\]
        \newline
        For the Caputo-Fabrizio derivative, we obtain the following:
        \[ D^{0} f(x) = \frac{1}{1 - 0}  \int_{0}^{x} \exp\left(\frac{0}{1 -0}(x-t)\right) f'(t) dt = \int_{0}^{x}f'(t) dt = f(x).\]
        \newline
        Finally, for the Riemann-Liouville derivative, we can simply make use of \autoref{r: integer} to note that in this context \(\alpha = 0\) is included in the natural integers. So \( \displaystyle D^\alpha = \frac{d^\alpha}{dx^\alpha} f(x) = {d^0}{dx^0} f(x) = f(x)\) by the first fundamental theorem of calculus.

        \item The proof for the Riemann-Liouville derivative is given by \cite{koning15}. And the proof for the Caputo-Fabrizio derivative is given by \cite{losada15}.For the Gr端nwald-Letnikov derivative, we get:
        \[ D^\alpha(D^\beta f(x)) = \lim_{h \to 0} \frac{1}{h^\alpha} \sum_{k=0}^\infty (-1)^k \binom{\alpha}{k} \left( \frac{1}{h^\beta} \sum_{l=0}^\infty (-1)^l \binom{\beta}{l} f(x - l h - kh)\right)\]
        \[= \lim_{h \to 0} \frac{1}{h^{\alpha + \beta}} \sum_{k=0}^\infty (-1)^k \binom{\alpha}{k} \sum_{l=0}^\infty (-1)^l \binom{\beta}{l} f(x - (k + l)h).\] We substitute \(m = k + l\) to deal with the double sums: 
        \[ \lim_{h \to 0} \frac{1}{h^{\alpha + \beta}} \sum_{m=0}^\infty f(x - mh)  \sum_{k=0}^m (-1)^k (-1)^{ m - k} \binom{\alpha}{k} \binom{\beta}{m - k}\] Now we make use of an identify from \autoref{s:appendices} to obtain:
        \[ = \lim_{h \to 0} \frac{1}{h^{\alpha + \beta}} \sum_{m=0}^\infty (-1)^m \binom{\alpha + \beta}{m} f(x - mh) = D^{\alpha + \beta} f(x).\]
        It can be shown in an exactly similar way that the latter expression is equal to \(D^\beta(D^\alpha f(x))\).

        
    \end{enumerate}
\end{proof}

\subsection{Proofs section \ref{s:MGF}}

\begin{proof}\label{p:negative}
    Let \(f_X(x) \sim \Gamma(\alpha, \lambda) =\) 
    \[\frac{x^{\alpha -1} e^{-\lambda x} \lambda^\alpha} {\Gamma(\alpha)}.\] This PDF is defined on \((0, \infty)\). So the function is not defined on \(\mathbb{R}\). This, however, is not a problem, as we can just evaluate the right limit. Since the Gamma function already uses \(\alpha\) as a parameter, we will evaluate \( \displaystyle \frac{f_X(x)}{|x|^\beta}, \beta > 0\):
    \[\lim_{x \to 0_+} \frac{f_X(x)}{|x|^\beta} = \lim_{x \to 0_+} \frac{x^{\alpha -1 - \beta} e^{-\lambda x} \lambda^\alpha} {\Gamma(\alpha)} = \lim_{x \to 0_+} \frac{x^{\alpha -(1 + \beta)} e^{-\lambda x} \lambda^\alpha} {\Gamma(\alpha)} .\] Thus for \(\alpha \geq \beta + 1, \lim_{x \to 0_+} \frac{f_X(x)}{|x|^\beta} < \infty\). Therefore, the first negative moment of the Gamma distribution should exist.

    We compute the first negative moment: 
    \[ \mathbb{E}[X^{-1}] = \int_{0}^{\infty} x^{-1} \frac{x^{\alpha -1} e^{-\lambda x} \lambda^\alpha} {\Gamma(\alpha)} dx = \frac{\lambda^\alpha}{\Gamma(\alpha)} \int_{0}^{\infty} x^{\alpha - 2} e^{-\lambda x} dx\]
    Using the substitution \(\displaystyle u = \lambda x, \frac{du}{dx} = \lambda, dx = \frac{du}{\lambda}\), we get:
    \[ = \frac{\lambda^\alpha}{\Gamma(\alpha)} \int_{0}^{\infty}\left(\frac{u}{\lambda}\right)^{\alpha -2} e^{-u} du = \frac{\lambda^\alpha}{\Gamma(\alpha) \lambda^{\alpha-1}} \int_{0}^{\infty}(\frac{u}{\lambda})^{\alpha -2} e^{-u} du.\] This integral is equal to \(\Gamma(\alpha - 1)\) (See Appendix \ref{s:appendices}). So we get: 
    \[\mathbb{E}[X^{-1}] = \frac{\lambda^\alpha \Gamma(\alpha - 1) }{\Gamma(\alpha) \lambda^{\alpha-1}} = \frac{\lambda \Gamma(\alpha - 1)}{(\alpha -1)\Gamma(\alpha - 1)} = \frac{\lambda}{(\alpha -1)}.\] Thus, for \(\alpha \neq 1, \mathbb{E}[X^{-1}] = \frac{\lambda}{(\alpha -1)}\). Fortunately, this is always the case, since we had just derived that the integral only converges when \(\alpha \geq \beta + 1, \text{ with } \beta > 0\). In other words, \(\alpha > 1\). So this holds.
\end{proof}

\begin{proof} Proof of Proposition \ref{t:mgf}

    \[M_X^{(n)}(t) = \frac{d^n}{dt^n} \int_{-\infty}^{\infty} e^{tx} f_X(x) dx = \int_{-\infty}^{\infty} \frac{d^n}{dt^n} e^{tx} f_X(x) dx\] (We can interchange differentiation and integration since all partial derivatives of \(e^{tx} f(x)\) are continuous and the absolute value of the integral converges, as we assume the \(n\)-th moment exists, see Appendix \ref{s:appendices}).
    \[ = \int_{-\infty}^{\infty} x^n e^{tx} f_X(x) dx, \text{evaluating at } t = 0: = \int_{-\infty}^{\infty} x^n e^{0x} f_X(x) dx\]
    \[ = \int_{-\infty}^{\infty} x^n f_X(x) dx = \mathbb{E}[X^n]\]
    The proof for the case that \(f_X(x)\) is discrete is very similar. In that case, one would have to change the order of the derivative and summation, which has also been justified in Appendix \ref{s:appendices}.
\end{proof}

\begin{proof}
    Proof of Proposition \ref{p: moments}
    \begin{enumerate}[(i)]
        \item This is trivial. For \(X\) a continuous random variable, we get: 
        \[ M_X^{(0)}(t) = \int_{-\infty}^{\infty} x^0 \cdot e^{t x } f_X(x) dx = \int_{-\infty}^{\infty} 1 \cdot e^{0 x } f_X(x) dx = \int_{-\infty}^{\infty} f_X(x) dx.\] Assuming that \(f(x)\) is a PDF, this integrates to 1 by definition. If this integral is not equal to 1, this implies that \(f(x)\) is not a PDF. The proof for the discrete case is the same but with a summation instead of an integral sign.
        \item \[M_{\mu + \sigma X}(t) = \mathbb{E}[e^{(\mu + \sigma X)t}] = \mathbb{E}[e^{\mu t} \cdot e^{\sigma X t}].\] Since this is the expectation of \(x\), every term that is not dependent on \(x\) can be taken out of the summation:
        \[ = e^{\mu t} \cdot \mathbb{E}[e^{\sigma X t}] = e^{\mu t} \cdot M_{ X}(\sigma t)\]
        \item 
        \[M_{X+Y}(t) = \mathbb{E}[e^{(X + Y)t}] = \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} e^{(x + y)t} f_{X, Y}(x, y) dx dy\] 
        \[= \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} e^{xt} \cdot e^{yt} f_{X, Y}(x, y) dx dy.\] 
        \(f_{X, Y}(x, y)\) is the joint pdf for \(X, Y\). But we know that the latter is equal to \(f_X(x) \cdot f_Y(y)\), if \(X, Y\) are independent. Thus we get:
        \[ = \left(\int_{-\infty}^{\infty}  e^{xt} f_X(x) dx\right) \left(\int_{-\infty}^{\infty}  e^{yt} f_Y(y) dy\right) = M_X(t) \cdot M_Y(t).\] 
    \end{enumerate}
\end{proof}

\begin{proof}
    Proof of Theorem \ref{t: negative}:
Suppose for the moment that \( X \) is a positive random variable. Since \( x \cdot f_X(x) \) is integrable for \( x > 0 \), we have:

\[
    \mathbb{E}(X) = \int_0^\infty x \, dF(x) = \int_0^\infty \int_0^\infty e^{tx} \, dt \, dF(x).
\]

We can interchange the order of integration as follows:

\[
    \mathbb{E}(X) = \int_0^\infty e^{tx} \, dF(x) \, dt = \int_0^\infty M_X(-t) \, dt.
\]

The interchange of the order of integration is subject to \( \mathbb{E}(e^{-tX}) \) being integrable from \( t = 0 \) to \( t = \infty \).

Finally, by substituting \( X^{-1} \) for \( X \), we find:

\[
    \mathbb{E}(X^{-1}) = \int_0^\infty M_X^{-1}(-t) \, dt.
\]

There are two natural ways to generalize (1) to \( \mathbb{E}(X^{-1}) \); one way gives:

\[
    \mathbb{E}(X^{-n}) = \int_0^\infty \int_0^\infty \cdots \int_0^\infty M_X(-t_n) \, dt_n \cdots dt_2 dt_1, \tag{2}
\]

while the second way gives:

\[
    \mathbb{E}(X^{-n}) = \frac{1}{\Gamma(n)} \int_0^\infty t^{n-1} M_X(-t) \, dt.
\]
\cite{cressie1981}
\end{proof}

\begin{proof}
    Proof Theorem \ref{t: MGF_accurate}
    We consider \(X\) to be a continuous variable. The three MGF expressions are accurate if \(\mathbb{E}[X^\alpha] - M_X^{(\alpha)}(0) = 0\), in other words, if 
    \[\int_{-\infty}^{\infty} (x^\alpha - D^\alpha e^{tx}) \cdot f_X(x) dx = 0 \iff x^\alpha = D^\alpha e^{tx}\]
    where \(D^\alpha\) the differential operator of order \(\alpha\). Note that we are taking derivatives w.r.t. \(t\), not \(x\). The proof will be shown for the Gr端nwald-left derivative.
    \begin{enumerate}[(i)]
        \item \[\leftindex_{GL}{M}_X^{(\alpha)} = D^\alpha_{GL}(e^{tx})  = \lim_{h \to 0} \frac{1}{h^\alpha} \sum_{k=0}^\infty (-1)^k \binom{\alpha}{k} \exp(x(t - kh))\]
        \[= \exp(xt) \lim_{h \to 0} \frac{1}{h^\alpha} \sum_{k=0}^\infty (-1)^k \binom{\alpha}{k} \exp(-xh)^k\]
        \[= \exp(xt) \lim_{h \to 0} \frac{1}{h^\alpha} (1 - \exp(-xh))^\alpha\]
        (where we used the binomial series identity defined in \ref{d: binomial}). Now we use the Taylor expansion of \(\exp(-xh) = 1 - xh + \frac{(xh)^2}{2!} - \frac{(xh)^3}{3!} + ... - ...\). Since \(h \to 0\), we get: \(\exp(-xh) = 1 - xh + \mathcal{O}(h^2)\) (the rest of the terms are negligible).
        Thus we get:
        \[ \exp(xt) \lim_{h \to 0} \frac{1}{h^\alpha} \left(1 -(1 - xh + \mathcal{O}(n))\right)^\alpha = \exp(xt) \lim_{h \to 0} \frac{1}{h^\alpha} \left(h(x + \mathcal{O}(h))\right)^\alpha \]
        \[ = \exp(xt) \lim_{h \to 0} \frac{1}{h^\alpha} \left(h^\alpha((x + \mathcal{O}(h)))^\alpha\right) = \exp(xt) \lim_{h \to 0} (x + \mathcal{O}(h))^\alpha\]
        \[ = \exp(xt) \cdot x^\alpha.\]
        Finally, we take a value of \(t\) around 0 and obtain \(\leftindex_{GL}{M}_X^{(\alpha)}(0) = x^\alpha\) 
        \item We consider the Riemann-Liouville derivative: 
        \[D_{RL}^\alpha(e^{tx}) = \frac{d^n}{dt^n} \frac{1}{\Gamma(n -\alpha)}  \int_{-\infty}^{t} (t-s)^{n - \alpha-1} \cdot e^{sx} ds\]
        \cite{koning15} has shown that this derivative is equal to \(x^\alpha e^{tx}\). Thus, if we take a value of \(t\) around 0, we get: \(\leftindex_{RL}{M}_X^{(\alpha)}(0) = x^\alpha\)
    \end{enumerate}

    The proof also holds for the case when \(X\) is a discrete random variable.
\end{proof}

\begin{proof}
    Proof of Theorem \ref{t: MGF_inaccurate}
    We compute \[\leftindex_{CF}{M}_X^{(\alpha)} = D^\alpha_{CF}(e^{tx}) = \frac{d^n}{dt^n}\frac{1}{1 - \beta}  \int_{-\infty}^{t} \exp\left(\frac{-\beta}{1 - \beta}(t - s)\right) x \exp(xs) ds\]
    \[= \frac{d^n}{dt^n}\frac{x}{1 - \beta} \exp\left(\frac{-\beta t}{1 - \beta}\right) \int_{-\infty}^{t} \exp\left(s\left(\frac{\beta }{1 - \beta} + x \right)\right) ds  \text{ where } \beta = \alpha - n \text{ and } n = \lfloor \alpha \rfloor.\]
    Now let \( \displaystyle u = \frac{\beta}{1 - \beta} + x\), so we get:
    \[\frac{d^n}{dt^n}\frac{x}{1 - \beta} \exp\left(\frac{-\beta t}{1 - \beta}\right) \int_{-\infty}^{t} \exp(us) ds = \frac{d^n}{dt^n}\frac{x}{1 - \beta} \exp\left(\frac{-\beta t}{1 - \beta}\right) \frac{1}{u} exp(us)\Big|_{-\infty}^{t}\]
    \[= \frac{x}{1 - \beta} \exp\left(\frac{-\beta t}{1 - \beta}\right) \cdot \frac{1}{u} \cdot \exp(u t) = \frac{x \exp(xt)}{(1 - \beta)x + \beta}\]
    Now we apply the derivative of the above expression, with respect to \(t\), \(n\) times:
    \[\frac{d^n}{d t^n} \frac{x \exp(xt)}{(1 - \beta)x + \beta} = \frac{x^{n+1} \exp(xt)}{(1 - \beta)x + \beta}\]
    Now we take a value of \(t\) around 0 and obtain:
    \[\leftindex_{CF}{M}_X^{(\alpha)} = D^\alpha_{CF}(e^{tx}) = \frac{x^{n+1} }{(1 - \beta)x + \beta}.\]
    The latter expression is not equal to \(x^\alpha\), thus the error of \(\leftindex_{CF}{M}_X^{(\alpha)}\) is:
    \[
    \begin{cases} 
    \displaystyle \int_{-\infty}^{\infty} x^\alpha  f_X(x) dx -  \displaystyle \int_{-\infty}^{\infty}  \frac{x^{n+1} }{(1 - \beta)x + \beta} f_X(x) dx & \text{if } X \text{ is continuous,} \\ 
    \displaystyle \sum_{i} \left(x_i^\alpha -  \frac{x_i^{n+1} }{(1 - \beta)x_i + \beta}\right) f_X(x_i) & \text{if } X \text{ is discrete.} 
\end{cases}\]

\end{proof}

\clearpage

\section{Appendix: Algorithms}\label{s:app_alg}
\begin{algorithm}[H]
\caption{Analyze Fractional Moments}
\label{alg:analyse_fractional_moments}
\begin{algorithmic}[1]
\REQUIRE Parameters: $\omega$, $\alpha$, $\beta$, list of horizons: $H\_values$, list of orders: $orders$, number of iterations: $n\_sim$
\ENSURE DataFrame of conditional moments for each $H$ and order
\STATE Initialize empty results DataFrame
\FOR{each $H$ in $H\_values$}
    \STATE $R_{H}^{2} \leftarrow$ SimulateConditionalVariance($\omega, \alpha, \beta, H, n\_sim$)
    \STATE $pdf\_R \leftarrow$ KDE distribution from $R_H^2$
    \FOR{each $order$ in $orders$}
        \STATE $empirical \leftarrow \text{mean}(|R_H^2|^{order})$
        \STATE $standard \leftarrow$ FractionalMoment($pdf\_R$, $order$, use\_abs=true)
        \STATE $CF \leftarrow$ FractionalMomentCF($pdf\_R$, $order$, use\_abs=true)
        \STATE Append $(H, order, empirical, standard, CF)$ to results
    \ENDFOR
\ENDFOR
\RETURN results
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Simulate Conditional Variance}
\label{alg:simulate_conditional_variance}
\begin{algorithmic}[1]
\REQUIRE Parameters: $\omega$, $\alpha$, $\beta$, list of horizons: $H\_values$, number of iterations: $n\_sim$
\ENSURE Array $R_H^2$ of accumulated conditional variances
\STATE Initialize $R_H^2$ as a zero array of length $n\_sim$
\STATE $\sigma_0^2 \leftarrow \omega / (1 - \alpha - \beta)$
\FOR{$i = 1$ to $n\_sim$}
    \STATE $\sigma^2 \leftarrow \sigma_0^2$
    \STATE $variance\_R_H \leftarrow 0$
    \FOR{$h = 1$ to $H$}
        \STATE $\sigma \leftarrow \sqrt{\sigma^2}$
        \STATE $r \sim \mathcal{N}(0, \sigma)$
        \STATE $variance\_R_H \leftarrow variance\_R_H + r^2$
        \STATE $\sigma^2 \leftarrow \omega + \alpha r^2 + \beta \sigma^2$
    \ENDFOR
    \STATE $R_H^2[i] \leftarrow variance\_R_H$
\ENDFOR
\RETURN $R_H^2$
\end{algorithmic}
\end{algorithm}


\begin{algorithm}
\caption{Compute $z$ from returns using GARCH and fractional moments}
\label{alg:compute_z}
\begin{algorithmic}[1]
\REQUIRE Parameters: $H \gets 2$, $n_{\text{sim}} \gets 100{,}000$, $\text{window} \gets 520$, $\text{target\_length} \gets$ \texttt{nothing}, returns, fractional order $\gamma$
\ENSURE Computed array \texttt{z}
\STATE 
\STATE $n \gets \text{length}(\texttt{returns})$
\STATE $\text{max\_index} \gets n - H$
\IF{$\text{target\_length} = \texttt{nothing}$}
    \STATE $\text{range} \gets \text{window} : \text{max\_index}$
\ELSE
    \STATE $\text{range} \gets (\text{max\_index} - \text{target\_length} + 1) : \text{max\_index}$
\ENDIF
\STATE Initialize empty array $z$
\FOR{each $t$ in \texttt{range}}
    \STATE $r_{\text{window}} \gets \texttt{returns}[(t - \text{window} + 1) : t]$
    \STATE Fit GARCH(1,1) model to $r_{\text{window}}$
    \STATE Extract parameters $\omega, \alpha, \beta$ from model
    \STATE $R_{H}^{2} \gets \text{simulate\_conditional\_variance}(\omega, \alpha, \beta, H, n_{\text{sim}})$
    \STATE $\text{distribution}_R \gets \text{kde}(R_{H}^{2})$
    \STATE $\text{pdf}_R \gets \text{KDEDistribution}(\text{distribution}_R)$
    \STATE $\text{moment} \gets \text{fractional\_moment}(\text{pdf}_R, \gamma; \text{use\_abs} = \text{true})$
    \STATE Append \texttt{moment} to \texttt{z}
\ENDFOR
\RETURN $z$
\end{algorithmic}
\end{algorithm}

\clearpage
\section{Appendix: Table of Common Distributions}\label{s:app_common_distributions}
\begin{table}[ht]
\renewcommand{\arraystretch}{1.5}
\begin{adjustwidth}{-.5in}{-.5in}
\begin{center}
    
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Distribution} & \textbf{PDF / PMF} & \textbf{MGF \(M_X(t)\)} & \textbf{Restrictions} \\
\hline

\( \text{Bernoulli}(p) \) & \(\displaystyle  f(x) = p^x(1-p)^{1-x} \) & \( M_X(t) = (1 - p) + pe^t \) & \( 0 \leq p \leq 1,\ x \in \{0,1\} \) \\
\hline

\( \text{Binomial}(n, p) \) & \( \displaystyle f(x) = \binom{n}{x} p^x (1-p)^{n-x} \) & \( M_X(t) = (1 - p + pe^t)^n \) & \( n \in \mathbb{N},\ 0 \leq p \leq 1 \) \\
\hline

\( \text{Poisson}(\lambda) \) & \( \displaystyle f(x) = \frac{\lambda^x e^{-\lambda}}{x!} \) & \( M_X(t) = \exp(\lambda(e^t - 1)) \) & \( \lambda > 0,\ x \geq 0 \) \\
\hline

\( \text{Exponential}(\beta) \) & \( \displaystyle f(x) = \frac{1}{\beta} e^{-x/\beta} \) & \( M_X(t) = \frac{1}{1 - \beta t},\ t < 1/\beta \) & \( \beta > 0,\ x > 0 \) \\
\hline

\( \text{Gamma}(\alpha, \beta) \) & \( \displaystyle f(x) = \frac{1}{\Gamma(\alpha)\beta^\alpha} x^{\alpha-1} e^{-x/\beta} \) & \( M_X(t) = (1 - \beta t)^{-\alpha},\ t < 1/\beta \) & \( \alpha, \beta > 0,\ x > 0 \) \\
\hline

\( \mathcal{N}(\mu, \sigma^2) \) & \( \displaystyle f(x) = \frac{1}{\sqrt{2\pi \sigma^2}} e^{-\frac{(x - \mu)^2}{2\sigma^2}} \) & \( M_X(t) = \exp\left( \mu t + \frac{\sigma^2 t^2}{2} \right) \) & \( \sigma > 0 \) \\
\hline

\end{tabular}
\end{center}
\end{adjustwidth}
\caption{Common distributions and their moment generating functions}
\label{t:MGFs_common}
\end{table}
